Staged Abstract Interpreter

### 2018-01-07 paper/paper.tex
fix typo

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis,
because it is interpreter and need the last k calling contexts as abstraction. 
But can we analyze programs (libraries) separately which generate the specialized 
analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.

>>>>

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis,
because it is interprocedural and need the last k calling contexts as abstraction. 
But can we analyze programs (libraries) separately which generate the specialized 
analysis and leave the k calling contexts as dynamic parameters, 
and then install these contexts when we have the whole program.
